Empirical normative theories

### 2020-07-25 simple.tex
Rm commands about prev defs

\begin{theorem}
	A normatively adequate and convincing empirical theory is valid.
\end{theorem}
\begin{proof}
	\NewDocumentCommand{\allhistsznp}{}{\mathscr{S}^{*, \ar_0}_{\not⇝ \phi}}
	\NewDocumentCommand{\allhistred}{}{\mathscr{S}^{*, \ar_0, \mathit{red}}_{\not⇝ \phi}}
	\NewDocumentCommand{\allhistnonred}{}{\mathscr{S}^{*, \ar_0, \mathit{irred}}_{\not⇝ \phi}}

	Given any $i \in I$ and $\phi \in \gPhi$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \phi$, and normative adequacy brings the conclusion.

>>>>

\begin{theorem}
	A normatively adequate and convincing empirical theory is valid.
\end{theorem}
\begin{proof}
	Given any $i \in I$ and $\phi \in \gPhi$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \phi$, and normative adequacy brings the conclusion.
